\section{Formal calculus}
    \subsection{Formal distributions and fields}
        \begin{definition}[Formal distributions] \label{def: formal_distributions}
            A \textbf{formal distribution} in $n$ variables $z_1, ..., z_n$ with coefficients in a vector space $U$ is an element of the vector space $U[\![z_1^{\pm}, ..., z_n^{\pm}]\!]$.
        \end{definition}
        It is very important to note that even when $U$ is an associative algebra, $U[\![z_1^{\pm}, ..., z_n^{\pm}]\!]$ is \textit{not} an algebra in general. This is because the coefficients of monomials in a product of the form:
            $$\left( \sum_{(i_1, ..., i_n) \in \Z^n} a_{i_1, ..., i_n} z_1^{i_1} ... z_n^{i_n} \right) \left( \sum_{(j_1, ..., j_n) \in \Z^n} b_{j_1, ..., j_n} z_1^{j_1} ... z_n^{j_n} \right)$$
        (wherein $a_{i_1, ..., i_n}, b_{j_1, ..., j_n} \in U$) are of the form:
            $$\sum_{(i_1, ..., i_n) \in \Z^n} \sum_{(j_1, ..., j_n) \in \Z^n} a_{i_1, ..., i_n} b_{j_1, ..., j_n}$$
        which, generally speaking, shall be an infinite sum.

        \begin{convention}
            Given any formal distribution:
                $$a(z) := \sum_{m \in \Z} a_m z^{-m - 1}$$
            let us write:
                $$a(z)^- := \sum_{m \in \Z_{\geq 0}} a_m z^{-m - 1}, a(z)^+ := \sum_{m \in \Z_{< 0}} a_m z^{-m - 1}$$
            with the point being that we would then have:
                $$(\del a(z))^{\pm} = \del( a(z)^{\pm} )$$
        \end{convention}
        \begin{definition}[Fields]
            
        \end{definition}
        \begin{definition}[Normal ordering] \label{def: normal_ordering}
            Given two formal distributions $a(w) \in U[\![w^{\pm 1}]\!], b(z) \in U[\![z^{\pm 1}]\!]$, let us define their \textbf{normally ordered product} to be:
                $$\order{ a(w) b(z) } := a(w)^+ b(z) + b(z) a(w)^-$$
        \end{definition}

    \subsection{Locality and Lie (super)algebras of formal distributions}
        Let us begin this subsection by introducing some computational tools, namely formal residues and Dirac distributions.
        \begin{definition}[Formal residues] \label{def: formal_residues}
            Let $U$ be vector space. Given a formal distribution $a(z_1, ..., z_n) := \sum_{(i_1, ..., i_n) \in \Z^n} a_{i_1, ..., i_n} z_1^{i_1} ... z_n^{i_n} \in U[\![z_1^{\pm}, ..., z_n^{\pm}]\!]$, let us define its \textbf{formal residue} to be:
                $$\Res_{z_1, ..., z_n} a(z_1, ..., z_n) := a_{-1, ..., -1}$$
        \end{definition}
        
        \begin{convention}
            As a shorthand, we will usually be writing:
                $$\del a(z_1, ..., z_n) := \sum_{i = 1}^n \frac{\del a(z_1, ..., z_n)}{\del z_i} dz_i$$
            for the total derivative of a formal distribution $a(z_1, ..., z_n)$.
        \end{convention}
        \begin{lemma}[Holomorphicity and integration by parts] \label{lemma: holomorphic_formal_distributions_and_integration_by_parts}
            Let $U$ be a vector space.
            \begin{enumerate}
                \item If $a(z_1, ..., z_n) \in U[z_1^{\pm 1}, ..., z_n^{\pm 1}]$ is a formal distribution, then:
                    $$\Res_{z_1, ..., z_n} \del a(z_1, ..., z_n) = 0$$
                \item If $a(z_1, ..., z_n), b(z_1, ..., z_n) \in U[z_1^{\pm 1}, ..., z_n^{\pm 1}]$ are formal distribution, then we will also have the following \say{integration by parts} formula:
                    $$\Res_{z_1, ..., z_n} (\del a(z_1, ..., z_n)) b(z_1, ..., z_n) = -\Res_{z_1, ..., z_n} (\del b(z_1, ..., z_n)) a(z_1, ..., z_n)$$
            \end{enumerate}
        \end{lemma}

        Formal residues allow us to define a non-degenerate bilinear pairing:
            $$\<-, -\>: U[\![z_1^{\pm}, ..., z_n^{\pm}]\!] \x \bbC[z_1^{\pm}, ..., z_n^{\pm}] \to U$$
        given by:
            $$\< a(z_1, ..., z_n), f(z_1, ..., z_n) \> := \Res_{z_1, ..., z_n} \left( a(z_1, ..., z_n) f(z_1, ..., z_n) \right)$$
        As Laurent polynomials $f(z_1, ..., z_n) \in \bbC[z_1^{\pm 1}, ..., z_n^{\pm 1}]$ have only finitely many summands with non-zero coefficients, the bilinear form $\<-, -\>$ is indeed well-defined. Non-degeneracy follows from the fact $\bbC$, being a field, contains no non-zero annihilator of elements of $U$. In any event, this means that we can view Laurent polynomials $f(z_1, ..., z_n) \in \bbC[z_1^{\pm 1}, ..., z_n^{\pm 1}]$ as test functions for formal distributions. In particular, these test functions are very useful for dealing with \textbf{formal Dirac distribution} (also called \textbf{formal delta distributions}). These are two-variable formal distributions given by:
            $$\1(w, z) := \sum_{m \in \Z} w^m z^{-m - 1} \in \bbC[w^{\pm 1}, z^{\pm 1}]$$
        \begin{convention}
            If $A$ is any operator, let us write:
                $$A^{[m]} := \frac{1}{m!} A^m$$
            for its \textbf{divided $m^{th}$ power}.
        \end{convention}
        \begin{lemma}[Basic properties of Dirac distributions] \label{lemma: basic_properties_of_dirac_distributions}
            Dirac distributions enjoy some very important properties.
            \begin{enumerate}
                \item For any Laurent polynomial $f(z) \in \bbC[z^{\pm 1}]$ (regarded by its image under the canonical embedding $\bbC[z^{\pm 1}] \subset \bbC[w^{\pm 1}, z^{\pm 1}]$), we have that:
                    $$\< \1(w, z), f(z) \> = f(w)$$.
                \item $\1(w, z) = \1(z, w)$. Furthermore, for any vector space $U$ and any formal distribution $a(z) \in U[z^{\pm}]$ (regarded by its image under the canonical embedding $\bbC[\![z^{\pm 1}]]\!] \subset \bbC[\![w^{\pm 1}, z^{\pm 1}]\!]$), we have that:
                    $$\1(w, z) a(z) = \1(z, w) a(w)$$
                In particular, we have the following important special case:
                    $$\1(w, z) \1(z, t) = \1(t, w) \1(w, z)$$
                with identifications $\bbC[\![z^{\pm 1}, t^{\pm 1}]\!] \cong \bbC[\![t^{\pm 1}, w^{\pm 1}]\!] \cong \bbC[\![w^{\pm 1}, z^{\pm 1}]\!]$ being made.
                \item The Dirac distribution has vanishing total derivative:
                    $$\del \1(w, z) = 0$$
                or, phrased differently, we have that:
                    $$\del_w \1(w, z) = -\del_z \1(w, z)$$
                \item Fix some $N \in \N$. Then:
                    $$
                        (z - w)^n \del_w^{[N]} \1(w, z) =
                        \begin{cases}
                            \text{$\del_w^{[N - n]} \1(w, z)$ if $N \leq n$}
                            \\
                            \text{$0$ if $n > N$}
                        \end{cases}
                    $$
            \end{enumerate}
        \end{lemma}

        Often, we will identify certain ostensibly transcendental functions with their Laurent series expansions, so that they may be regarded as formal distributions. More specifically, given a rational function:
            $$f(w, z) \in U(w, z)$$
        with values in some vector space $U$ and a \say{formal} pole at $w$, let us identify:
            $$f(w, z) = \sum_{m \in \Z_{\geq 0}} \del_w^{[m]} f(w, z) + \sum_{m \in \Z_{< 0}} \frac{1}{2\pi i} \oint_{\gamma_w} \frac{f(w, z)}{(z - w)^{m + 1}} dz$$
        where $\gamma_w$ is a closed and positively oriented contour centered at $w$. For instance, we have:
            $$\frac{1}{(z - w)^{j + 1}} = \sum_{m \in \Z_{\geq 0}} \binom{m}{j} w^{m - j} z^{-m - 1} - \sum_{m \in \Z_{< 0}} \binom{m}{j} w^{m - j} z^{-m - 1}$$
        as well as:
            $$\del_w^{[j]} \1(w, z) = \sum_{m \in \Z} \binom{m}{j} w^{m - j} z^{-m - 1}$$
    
        \begin{definition}[Locality] \label{def: locality}
            Let $U$ be a vector space. A formal distribution $a(w, z) \in U[\![w^{\pm 1}, z^{\pm 1}]\!]$ is said to be \textbf{local} if and only if there exists some sufficiently large $N \in \N$ such that:
                $$(z - w)^N a(w, z) = 0$$
                
            If $U$ is furthermore an associative algebra then we shall say that two formal distributions\footnote{We are implicitly identifying these with their images under the embeddings $U[\![w^{\pm 1}]\!] \subset U[\![w^{\pm 1}, z^{\pm 1}]\!] \supset U[\![z^{\pm 1}]\!]$.} $a(w) \in U[\![w^{\pm 1}]\!], b(z) \in U[\![z^{\pm 1}]\!]$ are \textbf{mutually local} if and only if the formal distribution $[a(w), b(z)] \in U[\![w^{\pm 1}, z^{\pm 1}]\!]$ is local in the sense above.
        \end{definition}
        \begin{remark}
            Let $U$ be an associative algebra. Since we know from lemma \ref{lemma: basic_properties_of_dirac_distributions} that:
                $$
                    (z - w)^n \del_w^{[N]} \1(w, z) =
                    \begin{cases}
                        \text{$\del_w^{[N - n]} \1(w, z)$ if $N \leq n$}
                        \\
                        \text{$0$ if $n > N$}
                    \end{cases}
                $$
            we see thus that a pair of formal distributions $a(w) \in U[\![w^{\pm 1}]\!], b(z) \in U[\![z^{\pm 1}]\!]$ are mutually local if and only if:
                $$[a(w), b(z)] \in \bbC \cdot \del_w^{[N]} \1(w, z)$$
            for some $N \in \N$. We also know that:
                $$
                    \begin{aligned}
                        \del_w^{[N]} \1(w, z) & = \sum_{m \in \Z} \binom{m}{N} w^{m - N} z^{-m - 1}
                        \\
                        & = \sum_{m \in \Z_{\geq 0}} \binom{m}{N} w^{m - N} z^{-m - 1} - \sum_{m \in \Z_{< 0}} \binom{m}{N} w^{m - N} z^{-m - 1}
                        \\
                        & = \frac{1}{(z - w)^{N + 1}}\bigg|_{|w| < |z|} + \frac{1}{(z - w)^{N + 1}}\bigg|_{|w| > |z|}
                    \end{aligned}
                $$
            and so $a(w), b(z)$ are mutually local if and only if:
                $$[a(w), b(z)] \sim \frac{1}{(z - w)^{N + 1}}$$
            for some $N \in \N$.
        \end{remark}

        